$Z^\prime$ mass limits and the naturalness of supersymmetry

### 2015-03-19 paper/e6ssm-tuning-paper.tex
remove comments.
updated acknowldgements to add Florian Staub and FS collaborators.

\begin{abstract}
%%The abstract.
%%Original abstract
%% title: Naturalness in U(1) extensions of the MSSM
% Copied SUSY2014 abstract.
%% With the discovery of a 125 GeV Standard Model (SM) like Higgs boson
%% and rising lower bounds on the masses of superpartners, minimal models
%% of low energy supersymmetry (SUSY) appear to be increasingly fine
%% tuned. In the Minimal Supersymmetric Standard Model (MSSM) large stop
%% masses, needed to obtain the observed Higgs mass, give a significant
%% contribution to fine tuning. $U(1)$ extensions of the MSSM that solve
%% the $\mu$-problem have new F- and D-term contributions to the Higgs
%% mass, allowing a 125 GeV Higgs with lighter stops and so alleviating
%% the associated fine tuning. However, it was recently demonstrated,
%% within a constrained version of the Exceptional Supersymmetric
%% Standard Model (E$_6$SSM) defined at the Grand Unification (GUT)
%% scale, that the presence of a massive $Z'$ boson introduces a
%% substantial new source of tuning in these theories at tree level. Here
%% we consider the impact of this tuning when we remove the fine tuning
%% that depends on assumptions about the SUSY breaking scale, by setting
%% the SUSY breaking parameters at low energies. We find that the
%% existing experimental bounds on the $Z'$ mass impose an effective
%% lower bound on the fine tuning, which does not depend on assumptions
%% about SUSY breaking.  We compare our results against the tuning in the
%% MSSM with the SUSY breaking terms also defined at low energies.

%%Alternative 1
%% Alt title: Probing natural SUSY in the most general way in the MSSM and U(1) extensions.

%% The discovery of a 125 GeV Standard Model (SM) like Higgs boson and
%% rising lower bounds on the masses of superpartners, have lead to
%% concerns that supersymmetric models are now fine tuned.  In the
%% Minimal Supersymmetric Standard Model (MSSM) large stop masses,
%% required for a $125$ GeV Higgs, also feed into the EWSB conditions
%% through renormalisation group equations forcing one to fine tune these
%% parameters to obtain the correct electroweak vacuum expectation
%% value. Nonetheless this fine tuning depends crucially on our
%% assumptions about the SUSY breaking scale.  Here we consider what fine
%% tuning may appear in supersymmetry at tree level, so that it is not so
%% dependent on assumptions about the SUSY breaking mechanism.  We focus
%% on U(1) extensions since these provide the most elegant solution to
%% the $\mu$-problem, which is also a naturalness issue, but we also
%% compare to the simplest SUSY model, the MSSM. In U(1) extensions anew
%% F- and D-term contributions raise the Higgs mass, allowing a $125$ GeV
%% Higgs with lighter stops which can alleviate this stop fine tuning in
%% models with SUSY breaking fixed at the high scale. However the
%% presence of a massive $Z'$ boson introduces a substantial new source
%% of tuning in these theories at tree level.  By choosing a low scale
%% boundary condition for where the SUSY breaking parameters are set we
%% compare how this tree level tuning compares to that of the MSSM where
%% chargino mass limits are the best way to probe tree level fine tuning,
%% by raising $\mu$ directly.  We find that the $Z^\tprime$ tuning places
%% more stringent limits on the fine tuning in most of the $U(1)$
%% extensions and that increasing $Z^\prime$ limits will challenge the
%% most natural scenarios of these models.

%% Alternative 2

%% Alt title: Z' mass limits and the naturalness of supersymmetry

@@

\acknowledgements
We would like to thank R. Nevzorov for many useful discussions and comments. DH would also like to thank A. Ismail and T. Rizzo. This work was supported by the University of Adelaide and by the ARC Centre of Excellence for Particle Physics at the Terascale.

@@

%% However for the results we present
%%  here we set the SARAH flag NoU1Mixing to true to avoid generating
%%  unmanageably large expressions.  It has previously been checked that
%%  when these models are evolved down from the GUT scale the radiatively
%%  generated gauge kinetic mixing gives an off diagonal gauge coupling,
%%  $g_{11}$ of just $\approx 0.02$ at the electroweak scale
%%  \cite{King:2005jy} and so it does not play a large role.

>>>>

\begin{abstract}

@@

\acknowledgements We would like to thank R. Nevzorov for many useful
discussions and comments and Florian Staub for very helpful responses
regarding the gauge kinetic mixing contributions in SARAH. DH would
also like to thank A. Ismail and T. Rizzo. PA would like to thank
J.H.~Park, A.~Voigt and D.~Stockinger for useful discussion regarding
the use of FlexibleSUSY in this project. This work was supported by
the University of Adelaide and by the ARC Centre of Excellence for
Particle Physics at the Terascale.

@@
